### 2021-04-23 input/experiments.tex
minors
mostly about implem
address easy stuff in experiments

This section aims at highlighting the properties of \NAME that enables
adaptive scoped broadcast in dynamic networks. It answers the
following questions: What is the overhead of reaching consistent
partitioning using \NAME in large scale networks? Does \NAME is
relevant in Edge infrastructures where \processes are geo-distributed
into clusters? We performed the experimentation using PeerSim, a
simulator written in Java that allows researchers to evaluate and
assess distributed algorithms in large scale
networks~\cite{montresor2009peersim}. The code is available on the
Github platform at
\TODO{\url{https://github.com/Chat-Wane/peersim-partition}}.

@@

\noindent We evaluate dynamic scoped broadcast. First, we create 100
partitions one at a time: before adding a new partition, consistent
partitioning must be reached. Second, we remove every partition one at
a time, in the order of their creation, hence starting from the first
and oldest partition that had been added.

@@

Figure~\ref{fig:complexity} shows the results of this experiment. The
top part of the figure shows the average traffic per \process per
second divided between $\alpha$ and $\delta$ messages. The bottom part
of the figure shows the time before reaching consistent partitioning.

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. The first partition is the most
expensive, for $\alpha$'s must reach every \process which takes time
and generate more traffic. Still, being reactive, as opposed as
cycle-based protocols~\cite{jelasity2007gossip}, \NAME quickly
converge towards consistent partitioning in only 350 milliseconds. The
last and $100^{th}$ partition added around 21 seconds is the least
expensive. By using scoped broadcast, control information only reaches
a small subset of the whole network.

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are more expensive than add operations. Indeed, the
top part of the figure shows that after 21 seconds, when the
experiment involves removals, traffic includes both $\alpha$'s and
$\delta$'s. The latter aims at removing stale information and
triggering competition while the former aims at updating shortest
paths. As corollary, the convergence time increases, for $\delta$'s
must reach every partition border before any sound competitors
propagate their partition. It is worth noting that this delete
operation involves concurrency: removals continue to propagate while
the competition is already partially triggered and propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system.  \NAME's overhead actually
depends on its usage.

@@

\noindent Figure~\ref{fig:geant} confirms that concurrent
\texttt{Add}s may reach consistent partitioning faster. In particular,
Figure~\ref{fig:geant} depicts a slow down in traffic around $500$ ms
due to the high latency inter-continental link. This link acts as a
bottleneck that does not exist when each cluster has its own source.

@@

\noindent Figure~\ref{fig:geant} shows that, when adding the
inter-continental link again, the two clusters can communicate
again. In the experiment involving one source for two clusters, it
generates traffic. After a $200$ milliseconds delay corresponding to
the new link latency, the cut off cluster starts to communicate
$\alpha$ messages again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic (only $2$
messages total), for \processes already know their closest source
located in their respective cluster.

\noindent Overall, this experimentation empirically demonstrates the
benefits of \NAME in the context of Edge infrastructures:
inter-connected autonomous systems where \processes may join or leave
or crash, communications links may be added or removed. \NAME coupled
with replication strategies designed for the Edge would allow locking
down the traffic of replica indexing, while providing every \processes
with quick access to replicated content.

>>>>

This section describes the results of our experimentation evaluating
the properties of \NAME that enables adaptive scoped broadcast in
dynamic networks. It answers the following questions: What is the
overhead of reaching consistent partitioning using \NAME in large
scale networks?  Does \NAME is relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\url{https://anonymous.4open.science/r/peersim-partition-5592}.

@@

\noindent We evaluate dynamic scoped broadcast. First, we create 100
partitions one at a time: \processes reach consistent partitioning
before we create each new partition. Second, we remove every partition
one at a time, in the order of their creation, hence starting from the
first and oldest partition that had been added.

@@

Figure~\ref{fig:complexity} shows the results of this experiment. The
top part shows the average traffic per \process per second divided
between $\alpha$ and $\delta$ messages. The bottom part shows the time
before reaching consistent partitioning.

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. The first partition is the most
expensive, for $\alpha$'s must reach every \process which takes time
and generate more traffic.  \NAME quickly converges towards consistent
partitioning in only 350 milliseconds. The last and $100^{th}$
partition added around 21 seconds is the least expensive. By using
scoped broadcast, control information only reaches a small subset of
the whole network.

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are more expensive than add operations. Indeed, the
top part of the figure shows that after 21 seconds, when the
experiment involves removals, traffic includes both $\alpha$'s and
$\delta$'s. The latter aims at removing stale information and
triggering competition while the former aims at updating shortest
paths. As corollary, the convergence time increases, for $\delta$
messages must reach every partition border before any sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals continue to propagate
while the competition is already partially triggered and propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system. In other words, \NAME's
overhead actually depends on its usage.

@@

\noindent Figure~\ref{fig:geant} confirms that concurrent
\texttt{Add}s may reach consistent partitioning faster. In particular,
the top part of Figure~\ref{fig:geant} depicts a slow down in traffic
around $500$ ms due to the high latency inter-continental link. The
first plateau corresponds to the source's autonomous system
acknowledging this source, while the second plateau corresponds to the
other autonomous system catching up.  The inter-continental link acts
as a bottleneck that does not exist when each cluster has its own
source.

@@

\noindent Figure~\ref{fig:geant} shows that, when adding the
inter-continental link again, the two clusters can communicate
again. In the experiment involving one source for two clusters, it
generates traffic. After a $200$ milliseconds delay corresponding to
the new link latency, the cut off cluster starts to communicate
$\alpha$ messages again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their
respective cluster.

\noindent Overall, this experimentation empirically demonstrates the
benefits of \NAME in the context of geo-distributed infrastructures,
e.g., inter-connected autonomous systems where \processes may join or
leave or crash, communications links may be added or removed. \NAME
coupled with replication strategies designed for the Edge would allow
locking down the traffic of replica indexing, while providing every
\process with quick access to replicated content.
